---
title: "CE_analysis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CE_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  fig.align = "center"
)
```

# Background

Person Level Economic Evaluations are implemented when a user has data at an individual level such that they have information for the cost and effect of a strategy for each individual. For example, when a clinical trial is run comparing a new treatment against the standard of care, researchers will have data on a certain clinical outcome (the 'effect') and the related costing data for each individual enrolled in the trial. As a result, the economic evaluation uses regression techniques to estimate the aggregate incremental cost effectiveness between the two different treatment arms. A detailed approach to regression techniques for cost effectiveness analysis is described here:

* Hoch et al., *Something old, something new, something borrowed, something blue: a framework for the marriage of health econometrics and cost-effectiveness analysis*, Health Economics, DOI:10.1002/hec.678

In this document, we will use an example dataset to arrive at an incremental cost effectiveness ratio (ICER) comparing the two strategies using the personlevelEE. 

## Example 1: Simulated Data

In this example, simulated individual level data comparing the status quo to a new multifactorial approach to prevent falls in the elderly. 
To arrive at an ICER, we will go through the following steps:

1. Defining a the cost vector in the dataset to get incremental cost. (`define_cost()`)
2. Defining a the effect vector in the dataset to get incremental effect. (`define_effect()`)
3. Defining any covariates in the dataset that could effect the differences in costs and effect and the resulting ICER. (`define_covariates()`)
4. Running an ICER model (`run_icer_model()`)
5. Plotting the ICER value on a C-E plane. 

```{r setup}
library(personlevelEE)
```

## Data 

The data can be loaded using the following command. 
Costs are related to individual usage of each program. Effect is percieved helpfulness of the program for each individual, a value between 0 and 100. 

```{r data}
data("data_example", package="personlevelEE")
```


We also have demographic data: age and sex for each individual.

## Incremental Cost and Effect

Before getting the incremental cost effectivness ratio, it is good practice to examine the incremental cost and effect for each strategy. To do this, we will use the `define_cost()` and `define_effect()` functions. These functions will perform a simple linear regression and a t-test to estimate the incremental costs and average costs per each group. 

First examine incremental costs. The `define_cost` function takes a vector of costs related to an individual id, and the associated treatment value. 
```{r}
cost_object <- define_cost(cost = data_example$cost, id = data_example$id, tx = data_example$tx)
print(cost_object)
```


The resulting output is a `define_cost` object (unique to `personlevelEE`) to facilitate visualization. The incremental costs can be viewed with a boxplot or barplot. 
```{r}
plot(cost_object, type = "barchart")
plot(cost_object, type = "boxplot")
```


The plot can be modified visually by adding `bw = TRUE`, for a more "publication friendly" format. 
Also, all plots in this package are `ggplot()` objects, so we can add (+) any of the normal ggplot adjustments to any plot. To do this, ggplot2 needs to be loaded with library(). A introduction to ggplot2 is available at https://ggplot2.tidyverse.org/.

Regression model diagnostics plots can be seen using the following command:
```{r}
plot(cost_object, type = "regression")
```


Incremental effects can be found in the same way. 
```{r}
effect_object <- define_effect(effect = data_example$effect, id = data_example$id, tx = data_example$tx)
print(effect_object)

## Plotting
plot(cost_object, type = "barchart")
plot(cost_object, type = "boxplot")
plot(cost_object, type = "regression")
```

## Adding Covariates

Since we have age and sex in our dataset and we believe that those factors can influence the resulting ICER, we will define them as covariates so we can use them in our final ICER regression model. 

THe function takes a list of the vectors for each covariate in the dataset. The *names* argument is the name of the covariate in the order listed. The *id* argument is used to link the individual's data throughout the package's functions. 
```{r}
covariates <- define_covariates(covariates = list(data_example$age,
                                                  data_example$sex),
                                names = c("age", "sex"), id = data_example$id)
covariates
```


## Getting an ICER

To get a value for icer we will use `run_icer_model()`. The regression results are printed using `print()`. The model will take the cost and effect object that we defined previously. The additional arguments are for covariates and including interaction terms. 

```{r}
icer_model <- run_icer_model(cost = cost_object, effect = effect_object,
                             covariates = covariates, interaction = FALSE)

print(icer_model)
```


A summary table can be formatted into a publication quality table using the `kableExtra` package.
```{r,message=FALSE,warning=FALSE}
library(kableExtra)
library(dplyr)
summary(icer_model)%>%
  kable() %>%
  kable_styling()
```

Additionally, we can plot the regression diagnostic plots by:
```{r}
plot(icer_model, type = "regression")
```

And we can view the ICER on a C-E plane by:
```{r}
plot(icer_model, type = "ce-plane")
```


