---
title: "Incremental Net Benefit Analysis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{INB_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  fig.align = "center"
)
```

## Introduction

This document will go over how to do an incremental net benefit analysis using the `personlevelEE()` package. A net benefit analysis starts with defining a willingness-to-pay threshold, a lambda ($\lambda$). At the individual level, net benefit is defined for each individual, $i$, in the dataset:
$$ NB_i = \lambda \cdot E_i - C_i$$
## Data
We will use the same data comparing the status quo to a new multifactorial approach to prevent falls in the elderly.
```{r setup}
library(personlevelEE)
data("data_example", package="personlevelEE")
```

## Define NB

Using the `define_NB()` function in the package, we can define a net benefit value for one or more $\lambda$'s. The `define_NB()` function takes the cost and effect objects from `define_cost()` and the `define_effect()` functions, respectively. 

```{r}
## get define_cost() and define_effect() objects()
cost_object <- define_cost(data_example$cost, data_example$id,
                           data_example$tx)

effect_object <- define_effect(data_example$effect, data_example$id,
                               data_example$tx)

```

Then, we can call `define_NB()` with different values of lambda as a vector of numbers:
```{r}
nb_value <- define_NB(lambdas = c(100, 350, 1000, 10000),
                      cost = cost_object, effect = effect_object)
```

## Run INB analysis

### Cost Effectiveness Acceptability Curve

