---
title: "Incremental Net Benefit Analysis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{INB_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  fig.align = "center")
options(rmarkdown.html_vignette.check_title = FALSE)
```

## Introduction

This document will go over how to do an incremental net benefit analysis using the `personlevelEE()` package. A net benefit analysis starts with defining a willingness-to-pay threshold, a lambda ($\lambda$). At the individual level, net benefit (NB) is defined for each individual, $i$, in the dataset by:
$$ NB_i = \lambda \cdot E_i - C_i$$
where, C & E are the individual cost and effect, respectively.


## Data
We will use data comparing the status quo to a new multifactorial approach to prevent falls in the elderly.
```{r setup}
library(personlevelEE)
data("data_example", package="personlevelEE")
head(data_example)
```

## Define NB

Using the `define_NB()` function in the package, we can define a net benefit value for one or more $\lambda$'s. The `define_NB()` function takes the cost and effect objects from `define_cost()` and the `define_effect()` functions, respectively. 

```{r}
## get define_cost() and define_effect() objects
cost_object <- define_cost(data_example, cost = cost, id = id, tx = tx)
effect_object <- define_effect(data_example, effect = effect, id = id, tx = tx)
```

Then, we can call `define_NB()` with different values of lambda as a vector of numbers:
```{r}
nb_value <- define_NB(lambdas = c(100, 350, 1000, 10000),
                      cost = cost_object, effect = effect_object)
```

## Run INB analysis

Using `run_INB_model()` we can run linear regression models for each willingness to pay value as defined in `define_nb()` in the form of:
$$ NB_\lambda = \beta_0 + \beta_1X_{trt}  $$ 
where $X_{trt}$ is a flag of treatment status.

We can add covariates to the model after defining them with `define_covariates()`. 

```{r}
## define covariates first
covariates <- define_covariates(data_frame = data_example, covariates_names = c("age", "sex"), id = id)

## run the model
nb_model <- run_INB_model(nb_values = nb_value, covariates = NULL)

print(nb_model)
```


We can plot the regression diagnostics, and other plots by modifying `type` (regression, barchart, or boxplot):
```{r warning = FALSE}
plot(nb_model, type = "regression")
plot(nb_model, type = "barchart")
```



### Cost Effectiveness Acceptability Curve

If we define more than one value for lambda, we can create a cost effectiveness acceptability curve based on the regression results. We can plot $1-p/2$ against the different values of $\lambda$, where p is the p-value associated with the coefficient on the treatment dummy ($X_{trt}$).

```{r}
plot(nb_model, type = "ceac")
```


