---
title: "Sensitivity Analysis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sensitivity_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  fig.align = "center")
options(rmarkdown.html_vignette.check_title = FALSE)
```

## Introduction
There are two types of sensitivity analyses (SA) that are typically explored: parametric and non-parametric. When we do parametric SA we assume that the distribution of our data is normal such that we can approximate the 95% confidence interval using Fieller's Theorem. On the other hand, re-sampling our data (or bootstrapping) is a non-parametric method of SA that does not assume any distribution of the data. 

Here is some additional references: [Willen & O'Brien 1996](https://pubmed.ncbi.nlm.nih.gov/8880166/); [Hoch 2006](https://pubmed.ncbi.nlm.nih.gov/16756680/); [Briggs 1998](https://pubmed.ncbi.nlm.nih.gov/9890333/); [Isaranuwatchai 2014](https://pubmed.ncbi.nlm.nih.gov/23728476/)


## Bootstrapping
To begin, let's do our bootstrapping. Bootstrapping will re-sample the data based on the cost and effect regressions. It will calculate a 95% confidence interval based on the 2.5% and 97.5% quantiles of the resulting sampling distribution. We also set a vector of lambdas such that we can calculate the proportion of re-sampled values that are cost effective at each lambda to plot for our cost effectiveness acceptability curve (CEAC).
```{r setup}
library(personlevelEE)
data("data_example", package="personlevelEE")
```

```{r}
## define cost & effect
cost_object <- define_cost(data_example, cost = cost, id = id, tx = tx)

effect_object <- define_effect(data_example, effect = effect, id = id, tx = tx)

## the arguments of the function include the number of repetitions (n), the values of lambda (or WTP)

bootstrap <- run_bootstrap(n=1000, cost = cost_object,
                           effect = effect_object, lambda_min = 10,
                           lambda_max = 10000, breaks = 4)
```

Plotting the results:
```{r}
plot(bootstrap, type = "cloud", bw =TRUE)
```

## CEAC
```{r}
plot(bootstrap, type = "ceac", bw = TRUE)
```



## Feiller's Theorem
For Feiller's theorem, we use a formula to calculate the upper and lower limit of a CI based on the assumption that both the cost and effect distributions are normal. 
```{r}
fieller <- define_fieller(cost = cost_object, effect = effect_object)
print(fieller) ## 95% confidence interval
```

Plotting the results:
```{r}
plot(fieller)
plot(fieller, CI = TRUE, bw = TRUE)
```


